Dismal Code: Studying the Evolution of Security Bugs

### 2013-04-07 docs/evol.tex
minor fixes

In this work we analyzed a large software repository to examine the behavior
of security bugs. Specifically, we analyzed more than 260GB of interdependent
projcet versions to see how security bugs evolve over time, their
persistence, and their relation with other bug categories and the size in
terms of bytecode. We have to mentioned that the versions examined were
actually releases of these projets. In essence, these {\sc jar}s were the ones
that were or still are out there in the wild, being used either as
applications, or dependencies of others.

>>>>

In this work we analyzed a large software repository to examine the behavior
of security bugs. Specifically, we analyzed more than 260GB of interdependent
projcet versions to see how security bugs evolve over time, their
persistence, and their relation with other bug categories and the size in
terms of bytecode. We have to mention that the versions examined were
actually releases of these projets. In essence, these {\sc jar}s were the ones
that were or still are, out there in the wild, being used either as
applications, or dependencies of others.
